---
title: "Vignette Title"
author: "Philip Bulsink"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
Setting up the database for initial data import must be done before beginning to add the data collected by `ds.compile_all_games()`. This vignette will assist in setting up PostgreSQL tables ready to accept the data.

# Installing PostgreSQL
Many examples and tutorials exist online for installing PostgreSQL, available with a simple Google search. One related to hockey analysis can be found [here](http://barloweanalytics.com/sqlstart.html), written by Matt Barlowe. If you follow the instructions listed there up until the 'Importing Data to the Database' section, you should be well set up. I'll suggest making a user named `hockey`, with the password `analytic`, and creating a `hockeystats` database for easiest use with the provided package code. Other users, passwords, or database names can easily be supplied as arguments to any of the written functions, though.

# Adding Tables
With the database pepared we can begin to add tables in which the data is stored. To add a table, each column must be named and provided with a data type. This can be done in a command as below, for the roster table: 

```{sql pbp, eval=FALSE}
CREATE TABLE roster(team_name varchar, team varchar, venue varchar, num_first_last varchar, game_date varchar, game_id integer, season integer, session varchar, player_number integer, team_num varchar, first_name varchar, last_name varchar, player_name varchar, name_match varchar, player_position varchar);
```

This command will run, and `CREATE TABLE` will print out if it is successful. We can check that the table has been added by searching for it in the output of the command `\dt`. More information on that table can be seen by typing `\d+ pbp`.

The other tables we'll start with are shifts, pbp, teams, and players. 
```{sql other_tables, eval=FALSE}
CREATE TABLE shifts(shift_number integer, game_period integer, shift_start varchar, shift_end varchar, shift_duration varchar, num_first_last varchar, team varchar, venue varchar, game_date varchar, game_id integer, season integer, session varchar, home_team varchar, away_team varchar, player_name varchar, team_num varchar, start_seconds real, end_seconds real);

CREATE TABLE pbp(season integer, game_id integer, game_date varchar, session varchar, event_index integer, game_period integer, game_seconds real, event_type varchar, event_description varchar, event_detail varchar, event_team varchar, event_player_1 varchar, event_player_2 varchar, event_player_3 varchar, event_length integer, coords_x integer, coords_y integer, players_substituted varchar, home_on_1 varchar,home_on_2 varchar, home_on_3 varchar, home_on_4 varchar, home_on_5 varchar, home_on_6 varchar, away_on_1 varchar, away_on_2 varchar, away_on_3 varchar, away_on_4 varchar, away_on_5 varchar, away_on_6 varchar, home_goalie varchar, away_goalie varchar, home_team varchar, away_team varchar, home_skaters integer, away_skaters integer, home_score integer, away_score integer, game_score_state varchar, game_strength_state varchar, highlight_code integer);

CREATE TABLE players(player_id integer, player_name_first varchar, player_name_last varchar, player_name_full varchar, player_jerseynum integer, player_position varchar, player_birth_date varchar, player_birth_city varchar, player_birth_country varchar, player_nationality varchar, player_height varchar, player_weight real, player_handedness varchar, is_active varchar, is_rookie varchar);

CREATE TABLE teams(team_id integer, team_name varchar, team_alias varchar, team_venue varchar, team_location varchar, team_city varchar, team_division_id integer, team_division_name varchar, team_conference_id integer, team_conference_name varchar, franchise_id varchar, is_active varchar);
```

As you calculate other statistics you can add more tables or add columns to these existing tables. Table operations should be performed before adding data to the tables. 

For example, to add a column for metric player weight to the players table, we could execute that command like this:
```{sql add_column, eval=FALSE}
ALTER TABLE players ADD COLUMN metric_weight varchar;
```

Once that column is added, you can go back to `R` to add data.

# Adding Data
There are some functions to aid in adding data you've scraped to the database. To start, you have to create a connection between `R` and the database. If your database user is `hockey`, password is `analytic` and database  name is `hockeystats` then this function needs no arguements. Otherwise, fill in the arguements by name as required.
```{r connect}
con <- db.get_db_connection()
```

With the connection available, you can begin to add data to the 
